A systematic search for transiting planets in the \KT\ data

### 2015-02-13 ms.tex
intro tweaks

The noise floor for \kepler\ data is often quoted as 15 parts per million per
six hours of observations \citep{Gilliland:2011}.
Although they generally do not influence the ability to search for transiting
planets, larger systematic effects exist on different timescales.
One of the most serious of these is spacecraft pointing: If the detector
flat-field is not known \emph{exquisitely}, then tiny changes to the relative
illumination of pixels caused by a star's motion in the focal plane will lead
to changes in the measured or inferred brightness of the star.

The pointing of \kepler\ was stable at the (LEVEL) level (citation) throughout
the primary mission.
This stability came to an end with the failure of a critical reaction wheel.
The \KT\ Mission \citep{Howell:2014} is a follow-on to the primary \kepler\
Mission, observing about a dozen fields near the ecliptic plane, each for
$\sim 75$ days at a time.
Because of the degraded spacecraft orientation systems, the new \KT\ data
exhibit far greater pointing variations---and substantially more
pointing-induced variations in photometry---than the original \kepler\ data.
This makes good data-analysis techniques even more valuable.

Good photometry relies on either a near-perfect flat-field
and pointing model or else data-analysis techniques that are
insensitive to such variations.
The flat-field for \kepler\ was measured on the ground before the launch of
the spacecraft, but is not nearly as accurate as required to make
pointing-insensitive photometric measurements at the relevant level of precision.
In principle direct inference of the flat-field might be possible;
however, because point sources are observed with relatively limited
spacecraft motion, and only a few percent of the data are actually stored and
downloaded to Earth, there isn't enough information in the data to derive or
infer a highly accurate flat-field map.
Therefore, work on \KT\ is sensibly focused on building data-analysis
techniques that are pointing-insensitive.

@@

The alternative to this approach is to simultaneously fit both the systematics
and the transit signals.
This method can push the detection limits to lower signal-to-noise while
robustly accounting for uncertainties about the systematic trends.
In particular, this allows us to \emph{marginalize} over choices in the noise
model and propagate any uncertainties to our confidence in the detection.
\dfmtodo{Do we need more about marginalization here?}

>>>>

The noise floor for \kepler\ data is often quoted as 15 parts per million (ppm) per
six hours of observations \citep{Gilliland:2011}.
Although they generally do not interfere with searches for transiting
planets, larger systematic effects exist on different timescales.
One of the most serious of these is spacecraft pointing: If the detector
flat-field is not known with very high accuracy, then tiny changes to the relative
illumination of pixels caused by a star's motion in the focal plane will lead
to changes in the measured or inferred brightness of the star.

The great stability of the original \kepler\ Mission
came to an end with the failure of a critical reaction wheel.
The \KT\ Mission \citep{Howell:2014} is a follow-on to the primary Mission,
observing about a dozen fields near the ecliptic plane, each for
$\sim 75$ days at a time.
Because of the degraded spacecraft orientation systems, the new \KT\ data
exhibit far greater pointing variations---and substantially more
pointing-induced variations in photometry---than the original \kepler\ Mission data.
This makes good data-analysis techniques even more valuable.

Good photometry relies on either a near-perfect flat-field
and pointing model or else data-analysis techniques that are
insensitive to these instrument properties.
The flat-field for \kepler\ was measured on the ground before the launch of
the spacecraft, but is not nearly as accurate as required to make
pointing-insensitive photometric measurements at the relevant level of precision.
In principle direct inference of the flat-field might be possible;
however, because point sources are observed with relatively limited
spacecraft motion, and only a few percent of the data are actually stored and
downloaded to Earth, there isn't enough information in the data to derive or
infer a complete or accurate flat-field map.
Therefore, work on \KT\ is sensibly focused on building data-analysis
techniques that are pointing-insensitive.

@@

The alternative to this approach is to \emph{simultaneously fit} both the systematics
and the transit signals.
Simultaneous fitting can push the detection limits to lower signal-to-noise while
robustly accounting for uncertainties about the systematic trends.
In particular, it permits us to \emph{marginalize} over choices in the noise
model and propagate any uncertainties about the systematic effects
to our confidence in the detection.
\dfmtodo{Do we need more about marginalization here?}
